Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-11-01 analysis/paper/paper.qmd
edit GIS maps

ggplot() +
  geom_sf(data = veg_all, aes(fill = veg_all$ecoregion)) + #add color for vegetation polygons
  geom_sf(data = pts_all, aes(color = pts_all$min_tcsa)) +
  theme_minimal()

ggplot(points_in_veg_zones_all) +
  aes(ecoregion,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

@@

ggplot() +
  geom_sf(data = veg_forest, aes(fill = Zone)) + #add color for vegetation polygons
  geom_sf(data = pts_forest,size = 3, aes(color = min_tcsa)) +
  theme_minimal()

@@

ggplot(points_in_veg_zones_forest_box) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

@@

>>>>

eco_plot <- ggplot() +
  geom_sf(data = veg_all, aes(fill = "grey")) +
   geom_sf_text(data = veg_all, aes(label = ecoregion), size =3.5)+
  geom_sf(data = pts_all, aes(color = min_tcsa)) +
  theme_minimal() +
  scale_fill_brewer(palette="Greys") +
  labs(color="TCSA") +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(size = 6))

eco_box <- ggplot(points_in_veg_zones_all) +
  aes(ecoregion,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

@@

for_plot <- ggplot() +
  geom_sf(data = veg_forest, aes(fill = "grey")) +
  geom_sf_text(data = veg_forest, aes(label = Zone), size =3.5)+
  geom_sf(data = pts_forest,size = 3, aes(color = min_tcsa)) +
  theme_minimal()+
  scale_fill_brewer(palette="Greys") +
  labs(color="TCSA") +
  guides(fill = FALSE)

@@

for_plot <- ggplot(points_in_veg_zones_forest_box) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

@@

plot_grid(eco_plot, for_plot, eco_box, for_plot, labels = c('A', 'C', 'B', 'D'))
```
